\documentclass[a4paper,8pt]{article}

\usepackage{parskip} 
\usepackage{hologo}
\usepackage{fontspec}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=.4in, bottom=.4in]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{2pt}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\color[HTML]{110223}

%for social icons
\usepackage{fontawesome5}

% For underline
\usepackage[normalem]{ulem}

\setmainfont{TeX Gyre Heros}  % Arial-compatible font available on all platforms

\begin{document}

% non-numbered pages
\pagestyle{empty} 


\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{1C033C} \Huge{Lokesh J} \\[6pt]
\\
\textcolor[HTML]{371e77}{{{{\faMobile} 8072904177}} $|$}
\textcolor[HTML]{371e77}{{{{\faEnvelope} lokesh121100@gmail.com}} $|$}
\textcolor[HTML]{371e77}{\underline{{\raisebox{-0.05\height}{\faLinkedin} LinkedIn}} $|$}
\textcolor[HTML]{371e77}{\underline{{\raisebox{-0.05\height}{\faGithub} GitHub}} $|$}
\textcolor[HTML]{371e77}{\underline{{\raisebox{-0.05\height}{\faCode} Leetcode}}}
\end{tabularx}

\section{Skills Summary}
\color[HTML]{1C033C}\textbf{Microsoft SharePoint:} SharePoint Online (M365), SharePoint Administration, SharePoint Framework\\[3pt]
\color[HTML]{1C033C}\textbf{SharePoint Migration:} SPMT, ShareGate, On-Premises Migration, Pre/Post Migration Validation\\[3pt]
\color[HTML]{1C033C}\textbf{Microsoft Power Platform:} Power Apps, Power Automate, Power BI, Dataverse, Power Pages, Copilot Studio, Power Platform Admin Center\\[3pt]
\color[HTML]{1C033C}\textbf{Cloud Technologies:} Azure, Microsoft Entra ID, Azure Blob Storage, Azure Monitor, Microsoft Purview, Microsoft 365 Admin Center\\[3pt]
\color[HTML]{1C033C}\textbf{Technologies \& Tools:} VS Code, Graph Explorer, Microsoft Excel, Oracle SQL, MySQL\\[3pt]
\color[HTML]{1C033C}\textbf{API \& Integration:} Microsoft Graph API, REST APIs, OAuth 2.0, Webhooks, MCP\\[3pt]
\color[HTML]{1C033C}\textbf{DevOps:} Azure DevOps, GitHub/Git, CI/CD Pipelines, PnP PowerShell, PAC CLI\\[3pt]

%Experience
\section{Work Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{{Spire.AI}} \hfill \color[HTML]{371e77} February 2025 - Present \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Data Analyst}}\ \hfill \color[HTML]{4B28A4} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Gathered data from various sources (Google Analytics, Google Play Console, LinkedIn, databases) ensuring data integrity and accuracy.
        \item Cleaned and preprocessed raw data using Power Query and Python, improving data quality by 20\%.
        \item Created insightful visualizations using Power BI, enhancing stakeholder understanding by 30\% and facilitating data-driven decisions.
        \item Conducted A/B testing to assess business initiatives, providing actionable recommendations with an 80\% success rate.
        \item Generated comprehensive reports and dashboards, resulting in a 40\% increase in stakeholder engagement and effectively communicating complex analyses.
        \item Managed client accounts with a 98\% resolution rate, identifying improvements that increased client satisfaction by 20\%.
    \end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{{PwC}} \hfill \color[HTML]{371e77} June 2024 - December 2024 \\[4pt]
\color[HTML]{371e77}\textbf{\textit{Power BI Developer Intern}}\ \hfill \color[HTML]{4B28A4} \\[5pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Created a performance report to analyze trends and set KPIs, achieving actionable insights to improve customer satisfaction (3.40/5 rating).
        \item Analyzed data from 7043 customers, revealing a 26.54\% churn rate, and used DAX functions to drive retention strategies.
        \item Developed operational efficiency metrics and utilized data-driven approaches to reduce churn and improve retention.
        \item Delivered insights on gender representation, helping shape policies to promote workplace diversity.
    \end{itemize}
\end{minipage}
\end{tabularx}

% Education
\section{Education}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\color[HTML]{1C033C} \textbf{Vellore Institute of Technology} & \hfill \color[HTML]{371e77} May 2019 – June 2024 \\
\color[HTML]{371e77} M.SC Computational Statistics and Data Analytics & \hfill \color[HTML]{4B28A4} \textit{\textbf{GPA: 7.14}} \\
\end{tabularx}

% Projects
\section{Projects}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item \textbf{Sales Insights - Brick \& Mortar Business:} Designed a Power BI dashboard to analyze sales trends for AtliQ hardware goods. Provided insights on product performance that are projected to boost revenue by 7\% through data-driven decisions.
        \item \textbf{T20 World Cup Cricket Data Analytics:} Developed a Power BI report to identify top 11 players by scraping data from ESPNcricinfo. Cleaned data with Pandas and created an interactive dashboard to visualize player performance.
    \end{itemize}
    \end{minipage}
\end{tabularx}

% Certificates
\section{Certificates}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item \textbf{Agile Scrum Master:} Certified in Agile methodologies with a focus on Scrum framework to improve project management.
        \item \textbf{Google Data Analytics:} Completed Professional Certificate with skills in SQL, Tableau, and R for data sharing and analysis.
    \end{itemize}
\end{minipage}
\end{tabularx}

\end{document}
